\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{
  letterpaper,
  margin=1in
}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\begin{document}
    \begin{center}
    {\Huge \textbf{AstroStreet AR}}\\[0.3cm]
    {\Large README / User Manual}\\[0.2cm]
    \end{center}
    
    \section{Jira Project Link}
        \begin{center}
            \textbf{\href{https://cs3338g10.atlassian.net/jira/for-you}{https://cs3338g10.atlassian.net/jira/for-you}}
        \end{center}
    
    \section{Objective}
        \textit{AstroStreet AR} is a mobile AR game that overlays virtual asteroids and alien ships onto the player’s real environment, allowing the user to aim through the device’s camera and tap to shoot incoming targets. The objective is to provide an immersive, movement–based AR experience that combines physical exploration with quick-reaction gameplay.
    
    \section{Why This Software Matters}
        The project showcases how Augmented Reality technology can be applied to create a game. It provides players with an enjoyable, outdoor-compatible experience that encourages physical activity, enhances spatial awareness, and fosters interactive engagement with their environment.
        
    \section{Accessing the Game}
        \textit{AstroStreet AR} is currently available to select users who signed up for early beta testing access. Access will be available to a limited group of users who register during the specified testing period. Selected testers will receive an email with a TestFlight download link.
        
        Once final testing is completed and remaining bugs are resolved, the complete game will launch on both the Apple App Store and the Google Play Store.
        
\end{document}
